%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified 2017 by:
% Andreas Offenhaeuser (http://anoff.io)
% Now a LuaLateX template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{michael}{lihs}{software engineer}{git:4040299}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{\color{red}contact}
Tübingen, Germany
\href{mailto:michael.lihs@mailbox.org}{michael.lihs@mailbox.org}
\graytitle{web}{\href{http://lihsmi.ch}{lihsmi.ch}}
\graytitle{github}{\href{https://github.com/michaellihs}{gh/michaellihs}}
\graytitle{twitter}{\href{https://twitter.com/kaktusmimi}{@kaktusmimi}}
\graytitle{linkedin}{\href{https://www.linkedin.com/in/michael-lihs}{michael-lihs}}
\section{\color{red}languages}
\graytitle{native}{german}
\graytitle{professional}{english}
\graytitle{basic}{french}
\section{\color{red}craftsmanship}
Java, Golang, Python
Terraform, Azure,
Docker, Kubernetes
Infrastructure as Code,
Continuous Integration \& Delivery,
Software Testing
\section{\color{red}domains}
Cloud Solutions,
Backend Development,
Automotive Software Development,
Developer Experience,
Agile Transformation
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\color{red}experience}

%------------------------------------------------

\begin{entrylist}
\entry
{2023--present}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{CI/CD toolchain for ADAS software. Pipeline migration from Jenkins to GitLab. GitLab runner setup with Kubernetes. Bazel build automation. Establishing core principles for CI/CD. Consulting for Developer Experience. Developer platform engineering.

\skills{acquired skills}{Jenkins, GitLab CI, shell scripting, Docker, Bazel, Terraform, Helm, Continuous Integration}
}
\end{entrylist}
\begin{entrylist}
\entry
{2022}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{Improving processes around managing the in-vehicle networking for a large German truck company. Developer journey for in-vehicle software development. Service-based in-vehicle communication. API platform for in-vehicle APIs.

\skills{acquired skills}{CAN, some/ip, developer platforms, backstage, Python, pytest, XML, Autosar}
}
\end{entrylist}
\begin{entrylist}
\entry
{2021}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{Analysis of the in-vehicle software development process for a large German truck company. Extensive recommendations for improved developer efficiency.

\skills{acquired skills}{Value Stream Mapping, user interviews, Developer Experience, Team Toplogies}
}
\end{entrylist}
\begin{entrylist}
\entry
{2021}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{Big data platform for ingesting vehicle data. Infrastructure management with Pulumi on Azure Cloud. Rest service development with Python / Flask.

\skills{acquired skills}{Pulumi, Python, Azure Cloud, Azure DevOps pipelines, test automation with pytest, infrastructure testing}
}
\end{entrylist}
\begin{entrylist}
\entry
{2020--2021}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{Web application for managing software packages for in-vehicle software. Backend development with Golang. Azure infrastructure automation with Terraform and Azure DevOps. CI/CD pipelines with Azure DevOps. Kubernetes deployments.

\skills{acquired skills}{VueJS, Golang, Postgres, Terraform, Azure DevOps, Azure Cloud, Kubernetes, Helm}
}
\end{entrylist}
\begin{entrylist}
\entry
{2019--2020}
{Infrastructure consultant (client project)}
{Thoughtworks, Stuttgart DE}
{Building a large-scale development platform for in-vehicle software and backend services. End-2-end testing with HW-in-the-loop. Infrastructure deployment with Terraform on Azure. CI/CD pipelines on Azure DevOps. In-vehicle and cloud services with Golang. Consumer-driven contract tests.

\skills{acquired skills}{Azure, Terraform, Azure DevOps, Azure Cloud, Kubernetes, Helm, Golang, nvidia Jetson, some/ip, Golang, ServerSpec, shell scripting, Pact, test automation, hardware-in-the-loop, Docker, Developer Experience}
}
\end{entrylist}
\begin{entrylist}
\entry
{2016--2019}
{DevOps Engineer}
{Robert Bosch GmbH, Stuttgart DE}
{CI/CD for the core services of the Bosch IoT Cloud. Cloud service management with BOSH. Container-as-a-service with Kubernetes.

\skills{acquired skills}{Platform engineering, Cloud Foundry, Concourse, GitLab, Jenkins, Docker, Kubernetes, Java, Golang, Spring Boot, Groovy, Ansible, shell scripting, infrastructure testing, BOSH, Splunk, test-driven development}
}
\end{entrylist}
\begin{entrylist}
\entry
{2015--2016}
{E-Business Engineer}
{Robert Bosch GmbH, Stuttgart DE}
{Microservice development and CI/CD for connected vehicles.

\skills{acquired skills}{Java, Jenkins, GitLab, Cloud Foundry, Spring Boot, RabbitMQ, Rest, Swagger, JIRA, Confluence, Linux system administration, Spark, Hadoop}
}
\end{entrylist}
\begin{entrylist}
\entry
{2009-2015}
{Web developer}
{Punkt.de GmbH, Karlsruhe DE}
{TYPO3 extension development with PHP. Infrastructure automation for the in-house data center. Deployment automatisation with Jenkins and GitLab.

\skills{acquired skills}{PHP, Javascript, Ruby, Chef, Continuous Integration, BDD, TD, Scrum, FreeBSD system administration, MySQL, Apache solr}
}
\end{entrylist}
\begin{entrylist}
  \entry
  {2006-2009}
  {Web developer}
  {Library of the University of Karlsruhe (KIT), DE}
  {TCL/TK and PHP development for an in-house web framework and the KVK (Karlsruher virtueller Katalog).
  
  \skills{acquired skills}{TCL, PHP, software testing, SOAP, Linux basics}
  }
  \end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{\color{red}education}

\begin{entrylist}

\entry
{2004--2012}
{Diploma in Computer Sciences}
{University of Karlsruhe (KIT), DE}
{Specialisation in compiler engineering and database systems.
}

\entry
{2001--2004}
{Guitar Maker}
{Der Gitarrenladen, Weingarten DE}
{Learning to build acoustic guitars (steelstring and classical guitars). Became a "Gitarrenbau Geselle". Managed the shop IT, the website and the online shop.
}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Community work section
%----------------------------------------------------------------------------------------

\section{\color{red}community work}

\begin{entrylist}
  \entry
  {2015 - today}
  {\href{https://www.meetup.com/de-DE/devops-stuttgart/}{DevOps Stuttgart Meetup}}
  {Organiser and frequent speaker}


  \entry
  {2023 - today}
  {\href{https://www.meetup.com/de-DE/automotive-software-development/}{Automotive Software Development Stuttgart Meetup}}
  {Founder and organiser}

  \entry
  {2013 - 2015}
  {\href{https://www.meetup.com/de-DE/devops-karlsruhe/}{DevOps Karlsruhe Meetup}}
  {Founder and frequent speaker}

\end{entrylist}

\section{\color{red}recent talks}

\begin{entrylist}
  \entry
  {2021}
  {\href{https://2021.baselone.ch/speech.html?id=A0482ED6-27CD-4C1A-8305-6C2492B54A8D}{Pipelines for infrastructure automation}}
  {BaselOne 2021}


  \entry
  {2021}
  {\href{https://eventyay.com/e/fa96ae2c/session/6763}{Trunk-based development}}
  {FOSSASIA Summit 2021}

  \entry
  {2021}
  {\href{https://youtu.be/8Rf_x6GNNiM}{Agile Threat Modeling}}
  {Thoughtworks Meetup}

\end{entrylist}

\end{document}
